---
title: "In-class code Supreme Court Database (HW3)"
author: "Sabrina Nardin"
date: 6/20/2024
output: html_document
---

Load the libraries
```{r}
library(tidyverse)
```

Load the data using `read_csv()` and a relative path (notice the two data frames are located in the "data" folder). You only need to modify the file argument of this function. Label the imported data as `scdb_case` and `scdb_vote`
```{r}
scdb_case <- read_csv("data/scdb-case.csv")
scdb_vote <- read_csv("data/scdb-vote.csv")
```

Explore the data using functions such as `head`, `View`, `summary`, `glimpse`, etc. or any other suitable functions 
```{r}
#View(scdb_case)
#View(scdb_vote)

glimpse(scdb_case)
glimpse(scdb_vote)
```

Today in class, we will explore an example similar to HW3 questions. But first, let's demonstrate the use of the `relocate()` function that we discussed in previous lectures. `relocate()` moves variables to the front of a dataframe.  You will find this trick useful for large dataframes like those in HW3. For example, the code below moves the `majVotes` and `minVotes` variables to the front of the `scdb_case` dataset:
```{r}
scdb_case %>% relocate(majVotes, minVotes)
# remember to save this in a new df if you want to retain this order
```


In-class example: finding and filtering the Justices who decided the landmark *Brown v. Board of Education* case. How can we approach this task?

First, we need to identify which data to use: the answer is both! The name of the justices are in `scdb_vote`, while the name of the case is in `scdb_case`. In the actual homework, there is only one question (in task 3) for which is essential to join the two dataframes; however, you might also consider joining data for the open question of task 3! 

Check the documentation: http://scdb.wustl.edu/documentation.php?s=1

Find the name of the justices: there are three different methods to code this
```{r}
# 1 with group_by and summarize (longest)
scdb_vote %>%
  group_by(justice, justiceName) %>%
  summarize(count = n()) %>% 
  print(n = 117)  

# run this code in the console to see full output with the 117 justices
# in the actual homework, please do not submit long outputs (comment it out)! we do not need it :) 
```


```{r}
# 2 with count (notice count() automatically reorders rows)
scdb_vote %>% count(justice, justiceName) %>% print(n = 117)
```

```{r}
# 3 with distinct (most straightforward)
scdb_vote %>% distinct(justice, justiceName)
```

Find the name of the case in the data (there are a lot of cases in this data frame: opening the data and scrolling through it  manually, like in Excel. is possible but not efficient; instead we can use R to help us restricting our search):
```{r}
# select(penguins, start_with("bill"))

# filter with criteria
scdb_case %>%
  relocate(caseName) %>%
  filter(str_starts(caseName, "BROWN"))

# search until you find the match and use it in next code (regular expressions with stringr will refine the search, we learn them later in the course)
```


```{r}
# this is the case we want: "BROWN et al. v. BOARD OF EDUCATION OF TOPEKA et al."
scdb_case %>% relocate(caseName) %>% filter(caseName == "BROWN et al. v. BOARD OF EDUCATION OF TOPEKA et al.")
```


Join the two dataframes:
```{r}
j <- scdb_case %>% 
  inner_join(scdb_vote)
```


And check who voted in the Brown case using the joined data:
Compare and double-check: https://www.nps.gov/brvb/learn/historyculture/justices.htm#:~:text=The%20nine%20justices%20serving%20on,no%20place%20in%20public%20schools.
```{r}
j %>% 
  relocate(caseName, justice, justiceName) %>% 
  filter(caseName == "BROWN et al. v. BOARD OF EDUCATION OF TOPEKA et al.") %>%
  distinct(caseName, justice, justiceName)
```


Finally, extract only the subset of justices who voted in that case. You can do it in two ways: `filter()` using the variable `justiceName` or with the variable `justice`
```{r}
# filter by justiceName
j %>% filter(justiceName %in% c("HLBlack", "WODouglas", "EWarren")) # add all justices who voted in that case

# filter by justice
j %>% filter(justice %in% c(78, 81, 90)) # add here all justices who voted in that case
```
